Symbolic Weighted Language Models and\\ Quantitative Parsing over Infinite Alphabets

### 2021-07-17 app-trees.tex

\noindent
We associate to $\hat\Omega$
a label theory $\hat{\Phi}$
like in Section~\ref{sec:SWVPA-def},
%
\noindent
and we define a linearization of trees of $\T_\Omega$ into
words of ${\hat\Omega}^*$ as follows:
\begin{description}
\item $\lin(a) = a$ for all $a \in \Omega_0$,
\item $\lin\bigl( b(t_1, \ldots, t_k)\bigr) =
       \call{b} \; \lin(t_1) \ldots \lin(t_k) \; \return{b}$
       when $b \in \Omega_k$ for $1 \leq k \leq M$.
\end{description}

@@

>>>>

\noindent
We associate to $\hat\Omega$
a label theory $\hat{\Phi}$
like in Section~\ref{sec:SWVPA-def},
%
\noindent
and we define a linearization of trees of $\T_\Omega$ into
words of ${\hat\Omega}^*$ as follows:
\begin{description}
\item $\lin(a) = a$ for all $a \in \Omega_0$,
\item $\lin\bigl( b(t_1, \ldots, t_k)\bigr) =
       \call{b} \; \lin(t_1) \ldots \lin(t_k) \; \return{b}$
       when $b \in \Omega_k$ for $1 \leq k \leq M$.
\end{description}
%
\begin{example}
The trees in Figure~\ref{fig:score-tree}
represent the two scores in Examples~\ref{ex:running},\ref{ex:nested-word}, 
and their linearization are respectively~$O$ and~$O'$ inn the same examples.
\end{example}

@@

\begin{figure}
\begin{center}
\begin{tikzpicture} [-,thick]
\tikzstyle{level 1}=[level distance=9mm,sibling distance=24mm]
\tikzstyle{level 2}=[level distance=8mm,sibling distance=6mm]
\tikzstyle{level 3}=[level distance=8mm,sibling distance=6mm]
\node {$\mathsf{m}$}
  child { node {$2$}
    child { node {$\mbox{\footnotesize A4}$} }
    child { node {$2$}
      child { node {$-$} }
      child { node {$2$}
        child { node {$\mbox{\footnotesize B4}$} }
        child { node {$\mbox{\footnotesize C$\sharp$5}$} }}}}
  child { node {$\mathsf{m}$}
    child { node {$3$}
      child { node {$\mbox{\footnotesize D5}$} }
      child { node {$\mbox{\footnotesize E5}$} }
      child { node {$\mbox{\footnotesize F5}$} }}
    child { node {$\varepsilon$} }};        
\end{tikzpicture}
%
\quad 
%
\begin{tikzpicture} [-,thick]
\tikzstyle{level 1}=[level distance=9mm,sibling distance=30mm]
\tikzstyle{level 2}=[level distance=8mm,sibling distance=8mm]
\tikzstyle{level 3}=[level distance=8mm,sibling distance=8mm]
\node {$\mathsf{m}$}
  child { node {$2$}
    child { node {$\mbox{\footnotesize A4}$} }
    child { node {$2$}
      child { node {$-$} }
      child { node {$\mbox{\footnotesize B4}$} } } }
  child { node {$\mathsf{m}$}
    child { node {$3$}
      child { node {$`\mbox{\footnotesize C$\sharp$5}`\,\mbox{\footnotesize D5}$} }
%                   {$\begin{array}{c}
%                     \mbox{\footnotesize C5}\\
%                     \mbox{\footnotesize D5}
%                     \end{array}$} }
      child { node {$\mbox{\footnotesize E5}$} }
      child { node {$\mbox{\footnotesize F5}$} } }
    child { node {$\varepsilon$} } };        
\end{tikzpicture}
\end{center}
\caption{Tree representation of scores 
of Examples~\ref{ex:running},\ref{ex:nested-word}, 
linearized respectively into~$O$ and~$O'$.}
\label{fig:score-tree}
\end{figure}

### 2021-07-17 introduction.tex

The output of parsing is a sequence of 
timed symbols $\nu\ts{\tau'}$ in an alphabet $\Delta$,
%events (or \emph{notes}) 
%in Common Western Music Notation (CWMN)~\cite{Gould11Notation}
where every symbol $\nu$ may represent 
an \emph{event} (or \emph{note}), 
specified by its \emph{pitch name} 
(\eg, $\mbox{\footnotesize A4}$, $\mbox{\footnotesize G5}$, \etc.), 
an event \emph{continuation} (symbol `$-$`, see Ex.~\ref{ex:SWT}),
or a \emph{markup}. %(\emph{parenthesis}),
The timestamp $\tau'$, expressed in number of \emph{measures},
belongs to a rhythmic ``grid'' obtained from recursive divisions:
whole notes ($\musWhole$) split in halves ($\musHalf$), halves
in quarters ($\musQuarter$), eights ($\musEighth$), \etc.
%
For instance, the output score 
\includegraphics[scale=0.35,trim=0 5mm 0 0]{pictures/ex1.pdf},
  %\includegraphics[scale=0.20]{pictures/score5.png}, 
corresponds to a hierarchical structure 
(measures, tuplets..., see Figure~\ref{fig:score-tree}) 
that can be linearized as the sequence
$O =$ 
$\ccall{\mathsf{m}}\ts{0}$,
$\ccall{2}\ts{0}$,
$\mbox{\footnotesize A4}\ts{0}$, 
$\ccall{2}\ts{\frac{1}{2}}$,
$-\ts{\frac{1}{2}}$,
$\ccall{2}\ts{\frac{3}{4}}$,
$\mbox{\footnotesize B4}\ts{\frac{3}{4}}$, 
$\mbox{\footnotesize C$\sharp$5}\ts{\frac{7}{8}}$, 
$\creturn{2}\ts{1}$,
$\creturn{2}\ts{1}$,
$\creturn{2}\ts{1}$,
$\ccall{\mathsf{m}}\ts{1}$,
$\ccall{3}\ts{1}$,
$\mbox{\footnotesize D5}\ts{1}$, 
$\mbox{\footnotesize E5}\ts{\frac{4}{3}}$, 
$\mbox{\footnotesize F5}\ts{\frac{5}{3}}$,
$\creturn{3}\ts{2}$,
$\creturn{\mathsf{m}}\ts{2}$,
$\creturn{\mathsf{m}}\ts{2}$.
%\end{enumerate}
The opening markups $\ccall{\mathsf{m}}$ %and $\creturn{\mathsf{m}}$
delimit \emph{measures}, 
which are time intervals of duration 1 in this example, 
while the subsequences of $O$ between markups 
$\ccall{d}$ and $\creturn{d}$,
for some natural number $d$, 
represent a division of the current 
time interval into $d$ sub-intervals of equal length.

\smallskip
We will show that $O$ is a solution for the
parsing of $I$. Note that several other parsings (e.g.,
\includegraphics[scale=0.35,trim=0 5mm 0 0]{pictures/ex2.pdf}) are possible.
SW-parsing associates a weight value
to each solution, and our framework
aims at selecting the best one with respect to this weight.
\endex
\end{example}

>>>>

The output of parsing is a sequence of 
timed symbols $\nu\ts{\tau'}$ in an alphabet $\Delta$,
%events (or \emph{notes}) 
%in Common Western Music Notation (CWMN)~\cite{Gould11Notation}
where every symbol $\nu$ may represent 
an \emph{event} (or \emph{note}), 
specified by its \emph{pitch name} 
(\eg, $\mbox{\footnotesize A4}$, $\mbox{\footnotesize G5}$, \etc.), 
an event \emph{continuation} (symbol `$-$`, see Ex.~\ref{ex:SWT}),
or a \emph{markup}. %(\emph{parenthesis}),
The timestamp $\tau'$, expressed in number of \emph{measures},
belongs to a rhythmic ``grid'' obtained from recursive divisions:
whole notes ($\musWhole$) split in halves ($\musHalf$), halves
in quarters ($\musQuarter$), eights ($\musEighth$), \etc.
%
For instance, the output score 
\includegraphics[scale=0.35,trim=0 5mm 0 0]{pictures/ex1.pdf},
  %\includegraphics[scale=0.20]{pictures/score5.png}, 
corresponds to a hierarchical structure 
(measures, tuplets..., see Figure~\ref{fig:score-tree}) 
that can be linearized as the sequence
$O =$ 
$\ccall{\mathsf{m}}\ts{0}$,
$\ccall{2}\ts{0}$,
$\mbox{\footnotesize A4}\ts{0}$, 
$\ccall{2}\ts{\frac{1}{2}}$,
$-\ts{\frac{1}{2}}$,
$\ccall{2}\ts{\frac{3}{4}}$,
$\mbox{\footnotesize B4}\ts{\frac{3}{4}}$, 
$\mbox{\footnotesize C$\sharp$5}\ts{\frac{7}{8}}$, 
$\creturn{2}\ts{1}$,
$\creturn{2}\ts{1}$,
$\creturn{2}\ts{1}$,
$\ccall{\mathsf{m}}\ts{1}$,
$\ccall{3}\ts{1}$,
$\mbox{\footnotesize D5}\ts{1}$, 
$\mbox{\footnotesize E5}\ts{\frac{4}{3}}$, 
$\mbox{\footnotesize F5}\ts{\frac{5}{3}}$,
$\creturn{3}\ts{2}$,
$\creturn{\mathsf{m}}\ts{2}$,
$\creturn{\mathsf{m}}\ts{2}$.
%\end{enumerate}
The opening markups $\ccall{\mathsf{m}}$ %and $\creturn{\mathsf{m}}$
delimit \emph{measures}, 
which are time intervals of duration 1 in this example, 
while the subsequences of $O$ between markups~$\ccall{d}$ and~$\creturn{d}$,
for some natural number~$d$, 
represent a division of the current 
time interval into $d$ sub-intervals of equal length.

\smallskip
We will show that $O$ is a solution for the
parsing of $I$. Note that several other parsings (\eg,
\includegraphics[scale=0.35,trim=0 5mm 0 0]{pictures/ex2.pdf}) are possible.
SW-parsing associates a weight value
to each solution, and our framework
aims at selecting the best one with respect to this weight.
\endex
\end{example}
